Human Deamination Read Length Analysis

### 2022-05-11 R/HumanDeaminationReadLengthAnalysis.rmd
Update HumanDeaminationReadLengthAnalysis.rmd

```{r CPD_mismatch__anchored_nucleotide_frequencies, fig.width = 11, fig.height = 7}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
                               title = "6-4 3' Anchored Nucleotide Frequencies Rep1",
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
                               title = "6-4 3' Anchored Nucleotide Frequencies Rep2",
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

@@

```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 7}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
                               title = "6-4 3' Anchored Purine Frequencies Rep1",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
                               title = "6-4 3' Anchored Purine Frequencies Rep2",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

@@

```{r compute_sequence_enrichment}
threePrimeMMAnchoredCPDEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceEnrichmentByReadLengthAndPos(mismatchDataRep[[i]],
                                            nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                            c("CG","CA","TG","TA"))
  }), names(mismatchDataRep))
}, threePrimeMismatchAnchoredCPDData, threePrimeMismatchCPDNucFreq, SIMPLIFY = FALSE)

fivePrimeMMAnchoredCPDEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceEnrichmentByReadLengthAndPos(mismatchDataRep[[i]],
                                            nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                            c("TGG"), posType = FIVE_PRIME)
  }), names(mismatchDataRep))
}, fivePrimeMismatchAnchoredCPDData, fivePrimeMismatchCPDNucFreq, SIMPLIFY = FALSE)

threePrimeMMAnchoredSixFourEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceEnrichmentByReadLengthAndPos(mismatchDataRep[[i]],
                                            nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                            c("CG","CA","TG","TA"))
  }), names(mismatchDataRep))
}, threePrimeMismatchAnchoredSixFourData, threePrimeMismatchSixFourNucFreq, SIMPLIFY = FALSE)

fivePrimeMMAnchoredSixFourEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceEnrichmentByReadLengthAndPos(mismatchDataRep[[i]],
                                            nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                            c("TGG"), posType = FIVE_PRIME)
  }), names(mismatchDataRep))
}, fivePrimeMismatchAnchoredSixFourData, fivePrimeMismatchSixFourNucFreq, SIMPLIFY = FALSE)
```

```{r plot_CPD_sequence_enrichment, fig.width = 11, fig.height = 7}
plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep1,
                       title = "CPD 3' Anchored YR Enrichment Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                       querySequences = c("CG","CA","TG","TA"))
plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep2,
                       title = "CPD 3' Anchored YR Enrichment Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                       querySequences = c("CG","CA","TG","TA"))

@@

@@

>>>>

```{r 6-4_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 7}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
                               title = "6-4 3' Anchored Nucleotide Frequencies Rep1",
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
                               title = "6-4 3' Anchored Nucleotide Frequencies Rep2",
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

@@

```{r 6-4_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 7}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
                               title = "6-4 3' Anchored Purine Frequencies Rep1",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
                               title = "6-4 3' Anchored Purine Frequencies Rep2",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

@@

```{r compute_sequence_enrichment}
threePrimeMMAnchoredCPDEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
                                      nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                      c("CG","CA","TG","TA"))
  }), names(mismatchDataRep))
}, threePrimeMismatchAnchoredCPDData, threePrimeMismatchCPDNucFreq, SIMPLIFY = FALSE)

fivePrimeMMAnchoredCPDEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
                                      nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                      c("TGG"), posType = FIVE_PRIME)
  }), names(mismatchDataRep))
}, fivePrimeMismatchAnchoredCPDData, fivePrimeMismatchCPDNucFreq, SIMPLIFY = FALSE)

threePrimeMMAnchoredSixFourEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
                                      nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                      c("CG","CA","TG","TA"))
  }), names(mismatchDataRep))
}, threePrimeMismatchAnchoredSixFourData, threePrimeMismatchSixFourNucFreq, SIMPLIFY = FALSE)

fivePrimeMMAnchoredSixFourEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
                                      nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                      c("TGG"), posType = FIVE_PRIME)
  }), names(mismatchDataRep))
}, fivePrimeMismatchAnchoredSixFourData, fivePrimeMismatchSixFourNucFreq, SIMPLIFY = FALSE)
```

```{r CPD_sequence_enrichment, fig.width = 11, fig.height = 7}
plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep1,
                       title = "CPD 3' Anchored YR Enrichment Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                       querySequences = c("CG","CA","TG","TA"))
plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep2,
                       title = "CPD 3' Anchored YR Enrichment Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                       querySequences = c("CG","CA","TG","TA"))

@@

```{r 6-4_sequence_enrichment, fig.width = 11, fig.height = 7}
plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep1,
                       title = "CPD 3' Anchored YR Enrichment Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                       querySequences = c("CG","CA","TG","TA"))
plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep2,
                       title = "CPD 3' Anchored YR Enrichment Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                       querySequences = c("CG","CA","TG","TA"))

plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment$rep1,
                       title = "CPD 5' Anchored TGG Enrichment Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
                       showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
                       querySequences = c("TGG"))
plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment$rep2,
                       title = "CPD 5' Anchored TGG Enrichment Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
                       showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
                       querySequences = c("TGG"))
```

@@

```{r compute_sequence_frequencies}
threePrimeMMAnchoredCPDSeqFreq = lapply(threePrimeMismatchAnchoredCPDData, function(mismatchDataRep) {
  lapply(mismatchDataRep, function(mismatchData) {
    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("CG","CA","TG","TA"))
  })
})

fivePrimeMMAnchoredCPDSeqFreq = lapply(fivePrimeMismatchAnchoredCPDData, function(mismatchDataRep) {
  lapply(mismatchDataRep, function(mismatchData) {
    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("TGG"), posType = FIVE_PRIME)
  })
})

threePrimeMMAnchoredSixFourSeqFreq = lapply(threePrimeMismatchAnchoredSixFourData, function(mismatchDataRep) {
  lapply(mismatchDataRep, function(mismatchData) {
    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("CG","CA","TG","TA"))
  })
})

fivePrimeMMAnchoredSixFourSeqFreq = lapply(fivePrimeMismatchAnchoredSixFourData, function(mismatchDataRep) {
  lapply(mismatchDataRep, function(mismatchData) {
    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("TGG"), posType = FIVE_PRIME)
  })
})
```

```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 7}
plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep1,
                        title = "CPD 3' Anchored YR Frequency Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
                        showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                        querySequences = c("CG","CA","TG","TA"))
plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep2,
                        title = "CPD 3' Anchored YR Frequency Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
                        showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                        querySequences = c("CG","CA","TG","TA"))

plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq$rep1,
                        title = "CPD 5' Anchored TGG Frequency Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
                        showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
                        querySequences = c("TGG"))
plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq$rep2,
                        title = "CPD 5' Anchored TGG Frequency Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
                        showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
                        querySequences = c("TGG"))
```

```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 7}
plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep1,
                        title = "CPD 3' Anchored YR Frequency Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
                        showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                        querySequences = c("CG","CA","TG","TA"))
plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep2,
                        title = "CPD 3' Anchored YR Frequency Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
                        showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                        querySequences = c("CG","CA","TG","TA"))

plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq$rep1,
                        title = "CPD 5' Anchored TGG Frequency Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
                        showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
                        querySequences = c("TGG"))
plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq$rep2,
                        title = "CPD 5' Anchored TGG Frequency Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
                        showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
                        querySequences = c("TGG"))
```
